---
title: "Final Analysis"
author: "Julien Christophe Piquet"
date: "15/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F)
```

## **Data formatting and path creation**

### **Geckos**

```{r data formatting & path creation (geckos)}
# Folder
folder<-"E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Research/Data/"
# Data creation
library(readxl)
data_geckos<-read_excel(paste0(folder,"data_geckos.xlsx"))
data_geckos<-data_geckos[data_geckos$sex=="FEM"|data_geckos$sex=="MAL",]
## Factor coding
data_geckos<-data_geckos[,-2]
data_geckos[,c(1,3:7,29)]<-lapply(data_geckos[,c(1,3:7,29)],as.factor)
## Removing odd observation 
data_geckos<-data_geckos[data_geckos$svl !=7.5,]
# Averaging toepad lamellas
data_geckos$lamella<-apply(data_geckos[,c(18:19)],1,mean)
```

### **Lizards**

```{r data formatting & path creation (lizards)}
library(readxl)

# Folder
folder<-"E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Research/Data/"
# Data creation
data_lizards<-read_excel(paste0(folder,"data_lizards.xlsx"))
data_lizards<-data_lizards[data_lizards$sex=="FEM"|data_lizards$sex=="MAL",]
## Factor coding
data_lizards[,c(1,3:7,30)]<-lapply(data_lizards[,c(1,3:7,30)],as.factor)
```

### **Skinks**

```{r data formatting & path creation (skinks)}
library(readxl)

# Folder
folder<-"E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Research/Data/"
# Data creation
data_skinks<-read_excel(paste0(folder,"data_skinks.xlsx"))
data_skinks<-data_skinks[data_skinks$sex=="FEM"|data_skinks$sex=="MAL",]
## Factor coding
data_skinks[,c(1,3:7,41)]<-lapply(data_skinks[,c(1,3:7,41)],as.factor)
```

## **Number of individuals**

```{r number individuals}
table(data_geckos$snakes)
table(data_lizards$snakes)
table(data_skinks$snakes)
```


## **Analysis of morphology**

### **Analysis of SVL**

#### **Geckos**

```{r analysis of SVL}
library(EnvStats)
library(DescTools)
library(chisq.posthoc.test)
library(glmmTMB)
library(DHARMa)
library(car)
library(multcomp)
library(emmeans)

tapply(data_geckos$svl,data_geckos$snakes,function(x) rosnerTest(log10(x),k=10)) # checking for outliers
plot(svl~sex,data=data_geckos)
plot(svl~snakes,data=data_geckos)
plot(svl~site,data=data_geckos)

# GLM with dispersion factor
glm_disp_svl_inter<-glmmTMB(log10(svl)~sex*snakes+(1|site),data=data_geckos,dispformula = ~site)
plotResiduals(simulateResiduals(glm_disp_svl_inter,n=1000))
testResiduals(simulateResiduals(glm_disp_svl_inter,n=1000))
Anova(glm_disp_svl_inter,type=2)
contrast(emmeans(glm_disp_svl_inter,~snakes|sex),adjust="fdr")
contrast(emmeans(glm_disp_svl_inter,~sex|snakes),adjust="fdr")
lapply(split(data_geckos,data_geckos$sex),function(x) tapply(x$svl,x$snakes,function(x) mean(x,na.rm=T)))
lapply(split(data_geckos,data_geckos$sex),function(x) tapply(x$svl,x$snakes,function(x) sd(x,na.rm=T)))
tapply(data_geckos$svl,data_geckos$snakes, mean)
tapply(data_geckos$svl,data_geckos$snakes, sd)

results_svl_geckos<-Anova(glm_disp_svl_inter,type=2)
results_svl_geckos<-do.call(rbind,results_svl_geckos)
results_svl_geckos<-t(as.matrix(results_svl_geckos))
write.csv(results_svl_geckos,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/results_svl_geckos.csv")

rm(list = setdiff(ls(),c("data_geckos","data_lizards","data_skinks","folder")))
```

#### **Lizards**

```{r analysis of SVL}
library(EnvStats)
library(DescTools)
library(chisq.posthoc.test)
library(glmmTMB)
library(DHARMa)
library(car)
library(multcomp)
library(emmeans)
tapply(data_lizards$svl,data_lizards$snakes,function(x) rosnerTest(log10(x),k=10)) # checking for outliers
plot(svl~sex,data=data_lizards)
plot(svl~snakes,data=data_lizards)
plot(svl~site,data=data_lizards)

# GLM with dispersion factor
glm_disp_svl_inter<-glmmTMB(log10(svl)~sex*snakes+(1|site),data=data_lizards,dispformula = ~site+sex)
plotResiduals(simulateResiduals(glm_disp_svl_inter,n=1000))
testResiduals(simulateResiduals(glm_disp_svl_inter,n=1000))
Anova(glm_disp_svl_inter,type=2)
contrast(emmeans(glm_disp_svl_inter,~snakes|sex),adjust="fdr")
contrast(emmeans(glm_disp_svl_inter,~sex|snakes),adjust="fdr")
lapply(split(data_lizards,data_lizards$sex),function(x) tapply(x$svl,x$snakes,function(x) mean(x,na.rm=T)))
lapply(split(data_lizards,data_lizards$sex),function(x) tapply(x$svl,x$snakes,function(x) sd(x,na.rm=T)))

results_svl_lizards<-Anova(glm_disp_svl_inter,type=2)
results_svl_lizards<-do.call(rbind,results_svl_lizards)
results_svl_lizards<-t(as.matrix(results_svl_lizards))
write.csv(results_svl_lizards,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/results_svl_lizards.csv")

rm(list = setdiff(ls(),c("data_geckos","data_lizards","data_skinks","folder")))
```

#### **Skinks**

```{r analysis of SVL}
library(EnvStats)
library(DescTools)
library(chisq.posthoc.test)
library(glmmTMB)
library(DHARMa)
library(car)
library(multcomp)
library(emmeans)
tapply(data_skinks$svl,data_skinks$snakes,function(x) rosnerTest(log10(x),k=10)) # checking for outliers
plot(svl~sex,data=data_skinks)
plot(svl~snakes,data=data_skinks)
plot(svl~site,data=data_skinks)

# GLM with dispersion factor
glm_disp_svl_inter<-glmmTMB(log10(svl)~sex*snakes+(1|site),data=data_skinks,dispformula = ~site+sex)
plotResiduals(simulateResiduals(glm_disp_svl_inter,n=1000))
testResiduals(simulateResiduals(glm_disp_svl_inter,n=1000))
Anova(glm_disp_svl_inter,type=2)
contrast(emmeans(glm_disp_svl_inter,~snakes|sex),adjust="fdr")
contrast(emmeans(glm_disp_svl_inter,~sex|snakes),adjust="fdr")

results_svl_skinks<-Anova(glm_disp_svl_inter,type=2)
results_svl_skinks<-do.call(rbind,results_svl_skinks)
results_svl_skinks<-t(as.matrix(results_svl_skinks))
write.csv(results_svl_skinks,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/results_svl_skinks.csv")

rm(list = setdiff(ls(),c("data_geckos","data_lizards","data_skinks","folder")))
```

### **Analysis of remaining morphological traits**

#### **Geckos**

```{r outliers}
library(glmmTMB)
library(rstatix)
library(car)
library(EnvStats)
library(naniar)
library(stringr)

# Checking for and removing outliers due to observer errors
morphology<-data_geckos[,c(8:15,18,19,30)]
morphology<-lapply(data_geckos[,c(8:15,18,19,30)],function(x) lm(log10(x)~log10(svl),data=data_geckos))
morphology<-lapply(morphology,"[[","residuals")
morphology<-morphology[-8]
names<-lapply(morphology,names)
names<-lapply(names,as.numeric)
morphology<-mapply(function(x,y) cbind(x,y),x=morphology,y=names)
morphology<-Reduce(function(x,y) merge(x,y,by="y",all=T),morphology)
colnames(morphology)<-c("id",names(data_geckos[,c(8:14,18,19,30)]))
morphology<-morphology[,-1]
factors<-data_geckos[,c(1:7)]
morphology<-merge(factors,morphology,by="row.names",all=T)
morphology<-morphology[,-1]
rosner_test<-lapply(morphology[,8:17],function(x) tapply(x,morphology$snakes,function(y) rosnerTest(y,k=10)))
# Removing outliers morphology
morphology$head_length[c(26,189,211,107,112)]<-NA
morphology$head_width[c(215,195,111)]<-NA
morphology$head_height[150]<-NA 
morphology$lfl[c(66,170,112,47)]<-NA
morphology$front_toe[c(47,143)]<-NA # 55 not included, does not seem error
morphology$lhl[c(112)]<-NA # 168 not included, does not seem error
morphology$hind_toe[236]<-NA # 130 not included, does not seem error
# Removing outliers data
data_geckos$head_length[c(121,47,67,195,2)]<-NA
data_geckos$head_width[c(70,52,199)]<-NA
data_geckos$head_height[233]<-NA 
data_geckos$lfl[c(158,3,2,140)]<-NA
data_geckos$front_toe[c(140,227)]<-NA # 148 not included, does not seem error
data_geckos$lhl[c(2)]<-NA # 28 not included, does not seem error
data_geckos$hind_toe[9]<-NA # 215 not included, does not seem error
rm(list = setdiff(ls(),c("data_geckos","data_lizards","data_skinks","folder")))
```

```{r morphology analysis}
library(glmmTMB)
library(effects)
library(DHARMa)
library(MASS)
library(gplots)
library(car)

lapply(data_geckos[,c(8:14)],function(x) plotmeans(x~sex,data=data_geckos))
lapply(data_geckos[,c(8:14)],function(x) plotmeans(x~site,data=data_geckos))
lapply(data_geckos[,c(8:14)],function(x) plotmeans(x~snakes,data=data_geckos))

models<-lapply(data_geckos[,c(8:14)],function(x) glmmTMB(log10(x)~log10(svl)+sex*snakes+(1|site),data=data_geckos,dispformula =~site))
lapply(models,function(x) plot(simulateResiduals(x,n=1000)))
lapply(models,function(x) testResiduals(simulateResiduals(x,n=1000)))
lapply(models,function(x) Anova(x,type=2))
results_geckos<-lapply(models,function(x) Anova(x,type=2))
results_geckos<-do.call(rbind,results_geckos)
lapply(models,function(x) contrast(emmeans(x,~snakes|sex), adjust="fdr"))
lapply(models,function(x) contrast(emmeans(x,~sex|snakes),adjust="fdr"))

write.csv(results_geckos,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/results_geckos.csv")

# Analysis of lamellae
with(data_geckos,cor.test(lamella,log10(svl),method="spearman"))
model_checking<-lapply(data_geckos[,c(18:19)],function(x) glmmTMB(x~log10(svl)+sex+(1|site),data=data_geckos,family=compois(link="log")))
lapply(model_checking,function(x) plot(simulateResiduals(x,n=1000)))
lapply(model_checking,function(x) Anova(x,type=2))

data_lamella<-aggregate(data_geckos$lamella,by=list(data_geckos$site,data_geckos$sex),function(x) mean(x,na.rm=T))
colnames(data_lamella)<-c("site","sex","lamella")
data_lamella$snakes<-substr(data_lamella$site,1,1)
data_lamella$snakes<-replace(data_lamella$snakes,data_lamella$snakes==1,"YES")
data_lamella$snakes<-replace(data_lamella$snakes,data_lamella$snakes==2,"NO")
lapply(split(data_lamella,data_lamella$sex),function(x) leveneTest(lamella~snakes,data=x))
lapply(split(data_lamella,data_lamella$sex),function(x) kruskal.test(lamella~snakes,data=x))
with(data_lamella,kruskal.test(lamella,snakes))

aggregate(data_lamella$lamella,by=list(data_lamella$snakes,data_lamella$sex),mean)
aggregate(data_lamella$lamella,by=list(data_lamella$snakes,data_lamella$sex),sd)

rm(list = setdiff(ls(),c("data_geckos","data_lizards","data_skinks","folder","morphology")))
```

#### **Lizards**

```{r outliers}
library(lme4)
library(rstatix)
library(car)
library(EnvStats)
library(naniar)

# Checking for and removing outliers due to observer errors
morphology<-data_lizards[,8:16]
morphology<-lapply(data_lizards[,8:16],function(x) lm(log10(x)~log10(svl),data=data_lizards))
morphology<-lapply(morphology,"[[","residuals")
morphology<-morphology[-9]
names<-lapply(morphology,names)
names<-lapply(names,as.numeric)
morphology<-mapply(function(x,y) cbind(x,y),x=morphology,y=names)
morphology<-Reduce(function(x,y) merge(x,y,by="y",all=T),morphology)
colnames(morphology)<-c("id",names(data_lizards[,c(8:15)]))
morphology<-morphology[,-1]
factors<-data_lizards[-c(30,32),c(1:7)]
morphology<-merge(factors,morphology,by="row.names",all=T)
morphology<-morphology[,-1]
rosner_test<-lapply(morphology[,8:15],function(x) tapply(x,morphology$snakes,function(y) rosnerTest(y,k=10)))
# Removing outliers from morphology
morphology$head_length[c(114,47,103)]<-NA
morphology$head_height[95]<-NA
morphology$snout_length[c(113,34)]<-NA
morphology$lfl[40]<-NA
morphology$front_toe[140]<-NA
morphology$lhl[c(68,62)]<-NA
morphology$hind_toe[c(96)]<-NA
# Removing outliers from data
data_lizards$head_length[c(76,142,66)]<-NA
data_lizards$head_height[59]<-NA
data_lizards$snout_length[c(75,131)]<-NA
data_lizards$lfl[136]<-NA
data_lizards$front_toe[100]<-NA
data_lizards$lhl[c(34,27)]<-NA
data_lizards$hind_toe[c(60)]<-NA
rm(list = setdiff(ls(),c("data_geckos","data_lizards","data_skinks","folder")))
```

```{r morphology analysis}
library(emmeans)
library(effects)
library(gplots)

lapply(data_lizards[,c(8:15)],function(x) plotmeans(x~sex,data=data_lizards))

models<-lapply(data_lizards[,c(8:15)],function(x) glmmTMB(log10(x)~log10(svl)+sex*snakes+(1|site),data=data_lizards,dispformula = ~site))
lapply(models,function(x) plot(simulateResiduals(x,n=1000)))
lapply(models,function(x) Anova(x,type=2))
results_lizards<-lapply(models,function(x) Anova(x,type=2))
results_lizards<-do.call(rbind,results_lizards)

write.csv(results_lizards,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/results_lizards.csv")

rm(list = setdiff(ls(),c("data_geckos","data_lizards","data_skinks","folder")))
```

#### **Skinks**

```{r outliers: skinks}
library(lme4)
library(rstatix)
library(car)
library(EnvStats)
library(naniar)

# Checking for and removing outliers due to observer errors
morphology<-data_skinks[,8:28]
morphology<-lapply(data_skinks[,8:28],function(x) lm(log10(x)~log10(svl),data=data_skinks))
morphology<-lapply(morphology,"[[","residuals")
morphology<-morphology[-16]
names<-lapply(morphology,names)
names<-lapply(names,as.numeric)
morphology<-mapply(function(x,y) cbind(x,y),x=morphology,y=names)
morphology<-Reduce(function(x,y) merge(x,y,by="y",all=T),morphology)
colnames(morphology)<-c("id",names(data_skinks[,c(8:22,24:28)]))
morphology<-morphology[,-1]
factors<-data_skinks[c(1:7)]
morphology<-merge(factors,morphology,by="row.names",all=T)
morphology<-morphology[,-1]
rosner_test<-lapply(morphology[,8:27],function(x) tapply(x,morphology$snakes,function(y) rosnerTest(y,k=10)))
# Removing outliers from morphology
morphology$front_toe[97]<-NA
morphology$hind_foot[c(58,97)]<-NA
morphology$lhl[c(22,58)]<-NA
morphology$pelvis_height[c(58)]<-NA
morphology$pelvis_width[c(29)]<-NA
morphology$body_width[c(29,100)]<-NA
morphology$body_length[c(52,33,38)]<-NA # 49 not included
# Removing outliers from data
data_skinks$front_toe[94]<-NA
data_skinks$hind_foot[c(59,94)]<-NA
data_skinks$lhl[c(26,59)]<-NA
data_skinks$pelvis_height[c(59)]<-NA
data_skinks$pelvis_width[c(32)]<-NA
data_skinks$body_width[c(32,97)]<-NA
data_skinks$body_length[c(53,36,40)]<-NA # 50 not included
rm(list = setdiff(ls(),c("data_geckos","data_lizards","data_skinks","folder")))
```

```{r mophological traits skinks}
library(emmeans)
library(effects)
library(glmmTMB)

lapply(data_skinks[,c(8:22,27)],function(x) plotmeans(x~sex,data=data_skinks))
lapply(data_skinks[,c(8:22,27)],function(x) plotmeans(x~site,data=data_skinks))
lapply(data_skinks[,c(8:22,27)],function(x) plotmeans(x~snakes,data=data_skinks))

models<-lapply(data_skinks[,c(8:22,27)],function(x) glmmTMB(log10(x)~log10(svl)+sex*snakes+(1|site),data=data_skinks))
lapply(models,function(x) plot(simulateResiduals(x,n=1000)))
lapply(models,function(x) Anova(x,type=2))
lapply(models[c(4,7)],function(x) contrast(emmeans(x,~snakes|sex),adjust="fdr"))
lapply(models[c(4,7)],function(x) contrast(emmeans(x,~sex|snakes),adjust="fdr"))

results_skinks<-lapply(models,function(x) Anova(x,type=2))
results_skinks<-do.call(rbind,results_skinks)
write.csv(results_skinks,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/results_skinks.csv")

aggregate(data_skinks[,c(8:22,27)],by=list(data_skinks$snakes),function(x) mean(x,na.rm=T))
aggregate(data_skinks$ufl,by=list(data_skinks$snakes,data_skinks$sex),function(x) mean(x,na.rm=T))
aggregate(data_skinks$front_toe,by=list(data_skinks$snakes,data_skinks$sex),function(x) mean(x,na.rm=T))

rm(list = setdiff(ls(),c("data_geckos","data_lizards","data_skinks","folder")))
```

## **Analysis of body condition and parasites**

### **Body condition**

#### **Geckos**

```{r body condition: geckos}
library(onewaytests)
library(glmmTMB)
library(gplots)
library(dplyr)
library(EnvStats)
library(DHARMa)
library(car)
library(emmeans)


bsma_geckos<-lm(log(weight)~log(svl),data=data_geckos)
bsma_geckos<-bsma_geckos$coefficients[2]/cor.test(log(data_geckos$weight),log(data_geckos$svl),method="pearson")$estimate
data_geckos$scaled_mass<-log(data_geckos$weight)*(mean(log(data_geckos$svl),na.rm=T)/log(data_geckos$svl))^bsma_geckos
tapply(data_geckos$scaled_mass,data_geckos$snakes,function(x) rosnerTest(x,k=10))
data_geckos$scaled_mass[c(146,207,239)]<-NA
homog.test(scaled_mass~sex,data=data_geckos,method="Levene")
welch.test(scaled_mass~sex,rate=0.1,data=data_geckos)
plotmeans(scaled_mass~sex,data=data_geckos)
model_bodycond<-glmmTMB(scaled_mass~sex*snakes+(1|site),data=data_geckos,dispformula =  ~site+sex)
plot(simulateResiduals(model_bodycond,n=1000))
Anova(model_bodycond,type=2)
results_bodycond_geckos<-Anova(model_bodycond,type=2)
results_bodycond_geckos<-do.call(rbind,results_bodycond_geckos)
results_bodycond_geckos<-t(as.matrix(results_bodycond_geckos))
write.csv(results_bodycond_geckos,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/table_bodycond_geckos.csv")
contrast(emmeans(model_bodycond,~snakes|sex),adjust="fdr")
contrast(emmeans(model_bodycond,~sex|snakes),adjust="fdr")
```

#### **Lizards**

```{r body condition: lizards}
library(onewaytests)
library(glmmTMB)
library(gplots)
bsma_lizards<-lm(log(weight)~log(svl),data=data_lizards)
bsma_lizards<-bsma_lizards$coefficients[2]/cor.test(log(data_lizards$weight),log(data_lizards$svl),method="pearson")$estimate
data_lizards$scaled_mass<-log(data_lizards$weight)*(mean(log(data_lizards$svl),na.rm=T)/log(data_lizards$svl))^bsma_lizards
tapply(data_lizards$scaled_mass,data_lizards$snakes,function(x) rosnerTest(x,k=10))
data_lizards$scaled_mass[c(38)]<-NA
homog.test(scaled_mass~sex,data=data_lizards,method="Levene")
welch.test(scaled_mass~sex,rate=0.1,data=data_lizards)
plotmeans(scaled_mass~sex,data=data_lizards)
model_bodycond<-glmmTMB(scaled_mass~sex*snakes+(1|site),data=data_lizards,dispformula =  ~site+sex)
plot(simulateResiduals(model_bodycond,n=1000))
Anova(model_bodycond,type=2)
results_bodycond_lizards<-Anova(model_bodycond,type=2)
results_bodycond_lizards<-do.call(rbind,results_bodycond_lizards)
results_bodycond_lizards<-t(as.matrix(results_bodycond_lizards))
write.csv(results_bodycond_lizards,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/table_bodycond_lizards.csv")
contrast(emmeans(model_bodycond,~snakes|sex),adjust="fdr")
contrast(emmeans(model_bodycond,~sex|snakes),adjust="fdr")
tapply(data_lizards$scaled_mass,data_lizards$sex,function(x) mean(x,na.rm=T))
```

#### **Skinks**

```{r body condition: creation (skinks)}
library(onewaytests)
library(glmmTMB)
library(gplots)
bsma_skinks<-lm(log(weight)~log(svl),data=data_skinks)
bsma_skinks<-bsma_skinks$coefficients[2]/cor.test(log(data_skinks$weight),log(data_skinks$svl),method="pearson")$estimate
data_skinks$scaled_mass<-log(data_skinks$weight)*(mean(log(data_skinks$svl),na.rm=T)/log(data_skinks$svl))^bsma_skinks
tapply(data_skinks$scaled_mass,data_skinks$snakes,function(x) rosnerTest(x,k=10))
homog.test(scaled_mass~sex,data=data_skinks,method="Levene")
welch.test(scaled_mass~sex,rate=0.1,data=data_skinks)
plotmeans(scaled_mass~sex,data=data_skinks)
model_bodycond<-glmmTMB(scaled_mass~sex*snakes+(1|site),data=data_skinks,dispformula =  ~site+sex)
plot(simulateResiduals(model_bodycond,n=1000))
Anova(model_bodycond,type=2)
results_bodycond_skinks<-Anova(model_bodycond,type=2)
results_bodycond_skinks<-do.call(rbind,results_bodycond_skinks)
results_bodycond_skinks<-t(as.matrix(results_bodycond_skinks))
write.csv(results_bodycond_skinks,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/table_bodycond_skinks.csv")
contrast(emmeans(model_bodycond,~snakes|sex),adjust="fdr")
contrast(emmeans(model_bodycond,~sex|snakes),adjust="fdr")
tapply(data_skinks$scaled_mass,data_skinks$snakes,mean)
```

### **Parasites**

#### *Geckos**

```{r mites: prevalence}
library(DHARMa)
library(glmmTMB)
glm_prevalence<-glmmTMB(mites_prev~sex*snakes+(1|site),data=data_geckos,family=binomial(link="logit"),dispformula = ~site)
plotResiduals(simulateResiduals(glm_prevalence,n=1000))
testResiduals(simulateResiduals(glm_prevalence,n=1000))
Anova(glm_prevalence,type=2)
results_prevalence_geckos<-Anova(glm_prevalence,type=2)
results_prevalence_geckos<-do.call(rbind,results_prevalence_geckos)
results_prevalence_geckos<-t(as.matrix(results_prevalence_geckos))
write.csv(results_prevalence_geckos,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/table_prevalence_geckos.csv")
table<-table(data_geckos$mites_prev,data_geckos$snakes)
table<-table/matrix(c(sum(table[,1]),sum(table[,1]),sum(table[,2]),sum(table[,2])),nrow=2,ncol=2)*100
table
(table(data_geckos[data_geckos$sex=="FEM",]$snakes,data_geckos[data_geckos$sex=="FEM",]$mites_prev)/apply(table(data_geckos[data_geckos$sex=="FEM",]$snakes,data_geckos[data_geckos$sex=="FEM",]$mites_prev),1,sum))*100
(table(data_geckos[data_geckos$sex=="MAL",]$snakes,data_geckos[data_geckos$sex=="MAL",]$mites_prev)/apply(table(data_geckos[data_geckos$sex=="MAL",]$snakes,data_geckos[data_geckos$sex=="MAL",]$mites_prev),1,sum))*100
```

```{r mites: intensity}
library(DHARMa)
rosnerTest(data_geckos$mites,k=10)
lapply(list(glmmTMB(mites~sex*snakes+(1|site),data=data_geckos,family=poisson(link="log"),dispformula = ~site),glmmTMB(mites~sex*snakes+(1|site),data=data_geckos,family=nbinom2(link="log"),dispformula = ~site)),AIC)
glm_abundance<-glmmTMB(mites~sex*snakes+(1|site),data=data_geckos,family=nbinom2(link="log"),dispformula = ~site)
plotResiduals(simulateResiduals(glm_abundance,n=1000))
testResiduals(simulateResiduals(glm_abundance,n=1000))
testZeroInflation(simulateResiduals(glm_abundance,n=1000))
Anova(glm_abundance,type=2)
results_abundance_geckos<-Anova(glm_abundance,type=2)
results_abundance_geckos<-do.call(rbind,results_abundance_geckos)
results_abundance_geckos<-t(as.matrix(results_abundance_geckos))
write.csv(results_abundance_geckos,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/table_abundance_geckos.csv")
contrast(emmeans(glm_abundance,~snakes|sex),adjust="fdr")
contrast(emmeans(glm_abundance,~sex|snakes),adjust="fdr")
tapply(data_geckos[data_geckos$sex=="FEM",]$mites,data_geckos[data_geckos$sex=="FEM",]$snakes,function(x) mean(x,na.rm=T))
tapply(data_geckos[data_geckos$sex=="FEM",]$mites,data_geckos[data_geckos$sex=="FEM",]$snakes,function(x) sd(x,na.rm=T))
tapply(data_geckos[data_geckos$sex=="MAL",]$mites,data_geckos[data_geckos$sex=="MAL",]$snakes,function(x) mean(x,na.rm=T))
tapply(data_geckos[data_geckos$sex=="MAL",]$mites,data_geckos[data_geckos$sex=="MAL",]$snakes,function(x) sd(x,na.rm=T))
```

#### *Lizards**

```{r mites: prevalence}
library(DHARMa)
library(glmmTMB)
glm_prevalence<-glmmTMB(mites_prev~sex*snakes+(1|site),data=data_lizards,family=binomial(link="logit"),dispformula = ~site)
plotResiduals(simulateResiduals(glm_prevalence,n=1000))
testResiduals(simulateResiduals(glm_prevalence,n=1000))
Anova(glm_prevalence,type=2)
results_prevalence_lizards<-Anova(glm_prevalence,type=2)
results_prevalence_lizards<-do.call(rbind,results_prevalence_lizards)
results_prevalence_lizards<-t(as.matrix(results_prevalence_lizards))
write.csv(results_prevalence_lizards,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/table_prevalence_lizards.csv")
table<-table(data_lizards$mites_prev,data_lizards$snakes)
table<-table/matrix(c(sum(table[,1]),sum(table[,1]),sum(table[,2]),sum(table[,2])),nrow=2,ncol=2)*100
table
(table(data_lizards[data_lizards$sex=="FEM",]$snakes,data_lizards[data_lizards$sex=="FEM",]$mites_prev)/apply(table(data_lizards[data_lizards$sex=="FEM",]$snakes,data_lizards[data_lizards$sex=="FEM",]$mites_prev),1,sum))*100
(table(data_lizards[data_lizards$sex=="MAL",]$snakes,data_lizards[data_lizards$sex=="MAL",]$mites_prev)/apply(table(data_lizards[data_lizards$sex=="MAL",]$snakes,data_lizards[data_lizards$sex=="MAL",]$mites_prev),1,sum))*100
```

```{r mites: intensity}
library(DHARMa)
rosnerTest(data_lizards$mites,k=10)
lapply(list(glmmTMB(mites~sex*snakes+(1|site),data=data_lizards,family=poisson(link="log"),dispformula = ~site),glmmTMB(mites~sex*snakes+(1|site),data=data_lizards,family=nbinom2(link="log"),dispformula = ~site)),AIC)
glm_abundance<-glmmTMB(mites~sex*snakes+(1|site),data=data_lizards,family=nbinom2(link="log"),dispformula = ~site)
plotResiduals(simulateResiduals(glm_abundance,n=1000))
testResiduals(simulateResiduals(glm_abundance,n=1000))
testZeroInflation(simulateResiduals(glm_abundance,n=1000))
Anova(glm_abundance,type=2)
results_abundance_lizards<-Anova(glm_abundance,type=2)
results_abundance_lizards<-do.call(rbind,results_abundance_lizards)
results_abundance_lizards<-t(as.matrix(results_abundance_lizards))
write.csv(results_abundance_lizards,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Tables_results/table_abundance_lizards.csv")
tapply(data_lizards$mites,data_lizards$snakes,mean)
tapply(data_lizards$mites,data_lizards$snakes,sd)
```
#### **Skinks**

```{r skink mites}
(table(data_skinks[data_skinks$sex=="FEM",]$snakes,data_skinks[data_skinks$sex=="FEM",]$mites_prev)/apply(table(data_skinks[data_skinks$sex=="FEM",]$snakes,data_skinks[data_skinks$sex=="FEM",]$mites_prev),1,sum))*100
(table(data_skinks[data_skinks$sex=="MAL",]$snakes,data_skinks[data_skinks$sex=="MAL",]$mites_prev)/apply(table(data_skinks[data_skinks$sex=="MAL",]$snakes,data_skinks[data_skinks$sex=="MAL",]$mites_prev),1,sum))*100
```

## **Building data for Veusz**

```{r Fig 3 and 4}
# Fig. 3

## Lizards
lizards_mean_morphology<-aggregate(data_lizards$svl,by=list(data_lizards$snakes,data_lizards$sex),function(x) mean(x,na.rm=T))
lizards_sd_morphology<-aggregate(data_lizards$svl,by=list(data_lizards$snakes,data_lizards$sex),function(x) sd(x,na.rm=T))
lizards<-cbind(lizards_mean_morphology,lizards_sd_morphology[,3])
colnames(lizards)<-c("snakes","sex","svl_mean","svl_sd")
write.csv(lizards,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Figures/Fig_morphology/lizards.csv")

## Skinks
skinks_mean_morphology<-aggregate(data_skinks[,c(11,14)],by=list(data_skinks$snakes,data_skinks$sex),function(x) mean(x,na.rm=T))
skinks_sd_morphology<-aggregate(data_skinks[,c(11,14)],by=list(data_skinks$snakes,data_skinks$sex),function(x) sd(x,na.rm=T))
skinks_mean_morphology_snakes<-aggregate(data_skinks[,c(15,17,18)],by=list(data_skinks$snakes),function(x) mean(x,na.rm=T))
skinks_sd_morphology_snakes<-aggregate(data_skinks[,c(15,17,18)],by=list(data_skinks$snakes),function(x) sd(x,na.rm=T))
skinks<-cbind(skinks_mean_morphology,skinks_sd_morphology[,3:4])
skinks_snakes<-cbind(skinks_mean_morphology_snakes,skinks_sd_morphology_snakes[,2:4])
colnames(skinks)<-c("snakes","sex",paste0(names(skinks[,3:4]),"_mean"),paste0(names(skinks[,5:6]),"_sd"))
colnames(skinks_snakes)<-c("snakes",paste0(names(skinks_snakes[,2:4]),"_mean"),paste0(names(skinks_snakes[,5:7]),"_sd"))
write.csv(skinks,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Figures/Fig_morphology/skinks.csv")
write.csv(skinks_snakes,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Figures/Fig_morphology/skinks_snakes.csv")

## Geckos
geckos_mean_morphology<-aggregate(data_geckos[,c(13,15,30)],by=list(data_geckos$snakes,data_geckos$sex),function(x) mean(x,na.rm=T))
geckos_sd_morphology<-aggregate(data_geckos[,c(13,15,30)],by=list(data_geckos$snakes,data_geckos$sex),function(x) sd(x,na.rm=T))
geckos<-cbind(geckos_mean_morphology,geckos_sd_morphology[3:5])
colnames(geckos)<-c("snakes","sex",paste0(names(geckos[,3:5]),"_mean"),paste0(names(geckos[,6:8]),"_sd"))
write.csv(geckos,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Figures/Fig_morphology/geckos.csv")

# Fig. 4

## Lizards
lizards_mean_bodycond<-aggregate(data_lizards$scaled_mass,by=list(data_lizards$snakes,data_lizards$sex),function(x) mean(x,na.rm=T))
lizards_sd_bodycond<-aggregate(data_lizards$scaled_mass,by=list(data_lizards$snakes,data_lizards$sex),function(x) sd(x,na.rm=T))
lizards<-cbind(lizards_mean_bodycond,lizards_sd_bodycond[,3])
colnames(lizards)<-c("snakes","sex","scaled_mass_mean","scaled_mass_sd")
lizards_mean_snakes<-aggregate(data_lizards$mites,by=list(data_lizards$snakes),function(x) mean(x,na.rm=T))
lizards_sd_snakes<-aggregate(data_lizards$mites,by=list(data_lizards$snakes),function(x) sd(x,na.rm=T))
lizards_snakes<-cbind(lizards_mean_snakes,lizards_sd_snakes[,2])
colnames(lizards_snakes)<-c("snakes","mites_mean","mites_sd")
write.csv(lizards,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Figures/Fig_condition/lizards.csv")
write.csv(lizards_snakes,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Figures/Fig_condition/lizards_snakes.csv")

## Skinks
skinks_mean_bodycond<-aggregate(data_skinks$scaled_mass,by=list(data_skinks$snakes,data_skinks$sex),function(x) mean(x,na.rm=T))
skinks_sd_bodycond<-aggregate(data_skinks$scaled_mass,by=list(data_skinks$snakes,data_skinks$sex),function(x) sd(x,na.rm=T))
skinks<-cbind(skinks_mean_bodycond,skinks_sd_bodycond[,3])
colnames(skinks)<-c("snakes","sex","scaled_mass_mean","scaled_mass_sd")
write.csv(skinks,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Figures/Fig_condition/skinks.csv")


## Geckos
geckos_mean_bodycond<-aggregate(data_geckos[,c(28,31)],by=list(data_geckos$snakes,data_geckos$sex),function(x) mean(x,na.rm=T))
geckos_sd_bodycond<-aggregate(data_geckos[,c(28,31)],by=list(data_geckos$snakes,data_geckos$sex),function(x) sd(x,na.rm=T))
geckos<-cbind(geckos_mean_bodycond,geckos_sd_bodycond[,3:4])
colnames(geckos)<-c("snakes","sex",paste0(names(geckos[,3:4]),"_mean"),paste0(names(geckos[,5:6]),"_sd"))
write.csv(geckos,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Figures/Fig_condition/geckos.csv")
```


## **Data for Table S1**

```{r table s1}
lizards_mean<-aggregate(data_lizards[,c(8:16,28,34)],by=list(data_lizards$snakes,data_lizards$sex),function(x) mean(x,na.rm=T))
colnames(lizards_mean)[2:ncol(lizards_mean)]<-c(paste0(names(lizards_mean[2:ncol(lizards_mean)]),"_mean"))
lizards_sd<-aggregate(data_lizards[,c(8:16,28,34)],by=list(data_lizards$snakes,data_lizards$sex),function(x) sd(x,na.rm=T))
colnames(lizards_sd)[2:ncol(lizards_sd)]<-c(paste0(names(lizards_sd[2:ncol(lizards_sd)]),"_sd"))
lizards_n<-aggregate(data_lizards[,c(8:16,28,34)],by=list(data_lizards$snakes,data_lizards$sex),function(x) length(x[complete.cases(x)]))
colnames(lizards_n)[2:ncol(lizards_n)]<-c(paste0(names(lizards_n[2:ncol(lizards_n)]),"_n"))
lizards<-cbind(lizards_mean,lizards_sd[,3:ncol(lizards_sd)],lizards_n[,3:ncol(lizards_n)])
skinks_mean<-aggregate(data_skinks[,c(8:23,27,42)],by=list(data_skinks$snakes,data_skinks$sex),function(x) mean(x,na.rm=T))
colnames(skinks_mean)[2:ncol(skinks_mean)]<-c(paste0(names(skinks_mean[2:ncol(skinks_mean)]),"_mean"))
skinks_sd<-aggregate(data_skinks[,c(8:23,27,42)],by=list(data_skinks$snakes,data_skinks$sex),function(x) sd(x,na.rm=T))
colnames(skinks_sd)[2:ncol(skinks_sd)]<-c(paste0(names(skinks_sd[2:ncol(skinks_sd)]),"_sd"))
skinks_n<-aggregate(data_skinks[,c(8:23,27,42)],by=list(data_skinks$snakes,data_skinks$sex),function(x) length(x[complete.cases(x)]))
colnames(skinks_n)[2:ncol(skinks_n)]<-c(paste0(names(skinks_n[2:ncol(skinks_n)]),"_n"))
skinks<-cbind(skinks_mean,skinks_sd[,3:ncol(skinks_sd)],skinks_n[,3:ncol(skinks_n)])
geckos_mean<-aggregate(data_geckos[,c(8:15,28,30,31)],by=list(data_geckos$snakes,data_geckos$sex),function(x) mean(x,na.rm=T))
colnames(geckos_mean)[2:ncol(geckos_mean)]<-c(paste0(names(geckos_mean[2:ncol(geckos_mean)]),"_mean"))
geckos_sd<-aggregate(data_geckos[,c(8:15,28,30,31)],by=list(data_geckos$snakes,data_geckos$sex),function(x) sd(x,na.rm=T))
colnames(geckos_sd)[2:ncol(geckos_sd)]<-c(paste0(names(geckos_sd[2:ncol(geckos_sd)]),"_sd"))
geckos_n<-aggregate(data_geckos[,c(8:15,28,30,31)],by=list(data_geckos$snakes,data_geckos$sex),function(x) length(x[complete.cases(x)]))
colnames(geckos_n)[2:ncol(geckos_n)]<-c(paste0(names(geckos_n[2:ncol(geckos_n)]),"_n"))
geckos<-cbind(geckos_mean,geckos_sd[,3:ncol(geckos_sd)],geckos_n[,3:ncol(geckos_n)])
write.csv(lizards,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Table S1/lizards.csv")
write.csv(skinks,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Table S1/skinks.csv")
write.csv(geckos,file="E:/Research/Projects/A_2019_CSIC_EvoImpLamp/Communication/Paper/Table S1/geckos.csv")
```

